---
title: "alternative matching"
date: "`r Sys.Date()`"
output: 
  html_document:
    code_folding: hide
---

```{r, message=FALSE, warning=FALSE}
library(dplyr)
library(Hmisc)
library(targets)

tar_load(m_panel)
tar_load(alt_m_panel)
```

## Difference between used and alternative matching

Alternative matching does not use surname as blocking variable and it enables different surnames (for all candidates without regard for their gender).
Original matching produces `r length(unique(alt_m_panel$person_id))` unique persons, alternative matching `r length(unique(alt_m_panel$person_id))` (`r round(length(unique(alt_m_panel$person_id)) / length(unique(m_panel$person_id))*100, 2)` % of original number).

```{r}
m_panel_candidacies <- m_panel %>% 
  count(person_id, candidate_gender) %>% 
  rename(n_candidacies = n) %>% 
  count(candidate_gender, n_candidacies) %>% 
  group_by(candidate_gender) %>% 
  mutate(pct = n / sum(n) * 100)

alt_m_panel_candidacies <- alt_m_panel %>% 
  count(person_id, candidate_gender) %>% 
  rename(n_candidacies = n) %>% 
  count(candidate_gender, n_candidacies) %>% 
  group_by(candidate_gender) %>% 
  mutate(pct = n / sum(n) * 100)


full_join(
  m_panel_candidacies %>% 
  group_by(candidate_gender) %>% 
  summarise(mean_candidacies = wtd.mean(n_candidacies, weights = n)),
  alt_m_panel_candidacies %>% 
  group_by(candidate_gender) %>% 
  summarise(alt_mean_candidacies = wtd.mean(n_candidacies, weights = n)), 
  by = "candidate_gender"
) %>% 
  mutate(diff = alt_mean_candidacies - mean_candidacies) %>% 
  knitr::kable(., digits = 3, 
               col.names = c("Gender", 
                             "Průměrný počet kandidatur (původní matching)",
                             "Průměrný počet kandidatur (alternativní matching)", 
                             "Rozdíl"))


```


```{r}

full_join(m_panel_candidacies %>% select(candidate_gender, n_candidacies, pct_old = pct), 
          alt_m_panel_candidacies %>% select(candidate_gender, n_candidacies, 
                                             pct_alt = pct), 
          by = c("candidate_gender", "n_candidacies")) %>% 
  mutate(diff_pp = pct_alt - pct_old) %>% 
  knitr::kable(., col.names = c("Gender", "N candidacies/person", "% persons (used matching)", "% persons (alt. matching)", "Difference"),
               digits = 3)

```


###
```{r}
m_panel2 <- m_panel %>% 
  mutate(candidate_gender2 = case_when(
    candidate_gender == "female" & candidate_age <= 50 ~ "female, under 50", 
    candidate_gender == "female" ~ "female, above 50",
    TRUE ~ "male"
  ))

alt_m_panel2 <- alt_m_panel %>% 
  mutate(candidate_gender2 = case_when(
    candidate_gender == "female" & candidate_age <= 50 ~ "female, under 50", 
    candidate_gender == "female" ~ "female, above 50",
    TRUE ~ "male"
  ))

m_panel_candidacies <- m_panel2 %>% 
  count(person_id, candidate_gender2) %>% 
  rename(n_candidacies = n) %>% 
  count(candidate_gender2, n_candidacies) %>% 
  group_by(candidate_gender2) %>% 
  mutate(pct = n / sum(n) * 100)

alt_m_panel_candidacies <- alt_m_panel2 %>% 
  count(person_id, candidate_gender2) %>% 
  rename(n_candidacies = n) %>% 
  count(candidate_gender2, n_candidacies) %>% 
  group_by(candidate_gender2) %>% 
  mutate(pct = n / sum(n) * 100)

full_join(m_panel_candidacies %>% select(candidate_gender2, n_candidacies, pct_old = pct), 
          alt_m_panel_candidacies %>% select(candidate_gender2, n_candidacies, 
                                             pct_alt = pct), 
          by = c("candidate_gender2", "n_candidacies")) %>% 
  mutate(diff_pp = pct_alt - pct_old) %>% 
  knitr::kable(., col.names = c("Gender", "N candidacies/person", "% persons (used matching)", "% persons (alt. matching)", "Difference"),
               digits = 3)

```

```{r}
full_join(
  m_panel2 %>% 
  count(person_id, candidate_gender2) %>% 
  rename(n_candidacies = n) %>% 
  count(candidate_gender2, n_candidacies) %>% 
  group_by(candidate_gender2) %>% 
  summarise(mean_candidacies_old = wtd.mean(n_candidacies, weights = n)), 
  alt_m_panel2 %>% 
  count(person_id, candidate_gender2) %>% 
  rename(n_candidacies = n) %>% 
  count(candidate_gender2, n_candidacies) %>% 
  group_by(candidate_gender2) %>% 
  summarise(mean_candidacies_alt = wtd.mean(n_candidacies, weights = n)), 
  by = "candidate_gender2"
) %>% 
  mutate(diff = mean_candidacies_alt - mean_candidacies_old) %>% 
  knitr::kable(., col.names = c("Gender", "Mean candidacies (used matching)", 
                                "Mean candidacies (alt. matching)", "Difference"), 
               digits = 3)

```

